\section{Abstract}
Biological soil crusts (BSC) cover a vast global area and are key components of
ecosystem productivity in arid soils. In particular, BSC contribute
significantly to the nitrogen (N) budget in arid ecosystems via N$^{2}$-fixation.
N2-fixation in mature crusts is largely attributed to heterocystous
cyanobacteria, however, early successional crusts are dominated by
non-heterocystous cyanobacteria and this suggests that microorganisms other
than cyanobacteria mediate N$^{2}$-fixation during the early stages of BSC
development. DNA stable isotope probing (DNA-SIP) with $^{15}$N$_{2}$ revealed
that \textit{Clostridiaceae} and \textit{Proteobacteria} are the most common
microorganisms to assimilate $^{15}$N in early successional 'light' crusts.
Incorporation of $^{15}$N$_{2}$ by cyanobateria was not observed. The maximum
relative abundance of $^{15}$N$_{2}$-assimilating taxa in the BSC was 0.00225\%
and 0.00127\% for taxa that belong to \textit{Clostridiaceae} and
\textit{Proteobacteria}, respectively. Their low abundance may
explain why these heterotrophic diazotrophs have not previously been
characterized in BSC.  Diazotrophs play a critical role in BSC formation and
characterization of these organisms represents a crucial step towards
understanding how antropogenic change will effect the formation and ecological
function of BSC in arid ecosystems.

%Heterocystous cyanobacteria relative abundance is correlated with mean annual
%temperature for \textit{Nostoc commune} MCT-1 and MFG-1, and \textit{Scytonema
%hyalinum} FGP-7A and DC-A (p-values 1.307x10$^{-02}$, 1.577x10$^{-06}$ and
%3.332x10$^{-03}$, 3.173x10$^{-04}$, respectively). However, the direction of
%the correlation is different for \textit{Nostoc} (decreasing with temperature)
%and \textit{Scytonema} (increasing with temperature) types.  

