\section{Results}
\subsection{Summary of Environmental Studies}
We included data from \citet{Garcia_Pichel_2013} and \citet{Steven_2013}
in the results to provide environmental context for the DNA-SIP
findings. Table~\ref{table:study_summary} summarizes the relevant background
information for the environmental data sets.
\begin{table}

\textbf{
\refstepcounter{table}
\label{table:study_summary}
Table \arabic{table}.
}
{Summary of contextual environmental data.} 

{\centering
\begin{tabular}{lp{6cm}p{6cm}}
\toprule
study & Description of samples & Number of samples \\ 
\midrule
\citet{Garcia_Pichel_2013} & Samples from ``light'', ``dark'' and ``lichen''
BSC across a wide geographic range in the southwestern United States and a site
mean annual temperature graient. & 23 samples total (9 dark, 12 light, 2
lichen) \\ \midrule 
\citet{Steven_2013} & Samples from three different soil types, ``sand'',
``shale'' and ``gypsum``. Both BSC samples and samples taken from sub-BSC soil
& 42 samples total (11 gypsum, 15 sand, 16 shale; 25 sub-BSC and 17 BSC) \\
\bottomrule
\end{tabular}}{}
\end{table}

\subsection{Comparison of sequence collections at "study"-level}
\subsubsection{Comparisons of OTU content:} Of the 4,340 OTU centroids
established for this study (including sequences from \citet{Steven_2013} and
\citet{Garcia_Pichel_2013}) 445 and 870 have matches in the Living Tree
Project (LTP) (a collection of 16S gene sequences for all sequenced type
strains \citep{Yarza_2008}) at greater or equal than 97\% and 95\% sequence
identity, respectively (LTP version 115). Similar numbers of total OTUs were
found in each data set explored in this study (i.e. the DNA-SIP data
presented here, the data presented by \citet{Steven_2013} and by
\citet{Garcia_Pichel_2013}). Specifically, there were 3,079 OTUs (209,354
total sequences after quality control) in the DNA-SIP data, 3,203 OTUs
(129,033 total sequences after quality control) in the
\citet{Garcia_Pichel_2013} study, and 2,481 OTUs (129,358 total sequences
after quality control) in the \citet{Steven_2013} study. The DNA-SIP data set
shares more OTUs with the \citet{Steven_2013} data (56\% of total OTUs from
combined dataset) than it does with the \citet{Garcia_Pichel_2013} data (46\%
of total OTUs from combined dataset). The \citet{Steven_2013} and
\citet{Garcia_Pichel_2013} data only share 46\% of OTUs.

\subsubsection{Comparisons of Taxonomic Content:} \textit{Cyanobacteria} and
\textit{Proteobacteria} were the top two phylum-level sequence annotations
for all three studies but only the DNA-SIP data had more
\textit{Proteobacteria} annotations than \textit{Cyanobacteria}.
\textit{Proteobacteria} represented the 29.8\% of sequence annotations in
DNA-SIP data as opposed to 17.8\% and 19.2\% for the
\citet{Garcia_Pichel_2013} and \citet{Steven_2013} data, respectively.
Figure~\ref{fig:study_phy_dist} shows the distribution of phylum-level
sequence annotations for each study in the nine most abundant  phyla across
all studies as determined by raw sequence counts. There is a stark contrast
in the total percentage of sequences annotated as \textit{Firmicutes} between
the raw environmental samples and the DNA-SIP data. \textit{Firmicutes}
represent only 0.21\% and 0.23\% of total phylum level sequence annotations
in the \citet{Steven_2013} and \citet{Garcia_Pichel_2013} studies,
respectively. In the DNA-SIP sequence collection \textit{Firmicutes} make up
19\% of phylum level sequence annotations. Also in sharp contrast for the
DNA-SIP versus environmental data is the number of putative heterocystous
\textit{Cyanobacteria} sequences. Only 0.29\% of \textit{Cyanobacteria}
sequences in the DNA-SIP data are annotated as belonging to "Subsection IV"
which is the heterocystous order of \textit{Cyanobacteria} in the Silva
taxonomic nomenclature \citep{17947321}. In the \citet{Steven_2013} and
\citet{Garcia_Pichel_2013} studies 15\% and 23\%, respectively, of
\textit{Cyanobacteria} sequences are annotated as belonging to "Subsection
IV".  

\subsection{Ordination of CsCl gradient fraction SSU rRNA libraries} Ordination
of Bray-Curtis \citep{Bray_1957} distances between CsCl gradient fraction
sequence libraries with principal coordinates analysis shows the labeled
gradient fraction libraries diverge from control at the ``heavy`` of the CsCl
gradients (Figure~\ref{fig:ordination}). When the labeled and control CsCl
gradient fraction 16S rRNA gene libraries are paired such that each pair
contains a control fraction and labeled fraction from the same incubation day
with a density difference below 0.003 g/mL, the Bray-Curtis distance between
the fraction pair is positively correlated to the density of the labeled
fraction (p-value: 0.00052, r$^{2}$: 0.3315) (inset
Figure~\ref{fig:ordination}).  Additionally, the label/control category for
heavy fractions is statistically significant by the Adonis test (p-value:
0.001, r$^{2}$: 0.136) \citep{Anderson_2001}. The first principal axis appears
to be correlated with fraction density (Figure~\ref{fig:ordination}) and the
Adonis test p-value for density versus pairwise Bray-Curtis distances with all
CsCl fraction libraries is 0.001 (r$^{2}$ 0.117).

\subsection{Identities of possible $^{15}$N incorporators} The OTUs that have
enriched proportion means in labeled gradient heavy fractions versus control
gradient heavy fractions are those that have incorporated the stable isotope
tracer into their DNA. We found 38 OTUs that appeared to incorporate $^{15}$N
into DNA (or ``responders''). Of these 38, 26 are annotated as
\textit{Firmicutes}, 9 as \textit{Proteobacteria}, 2 as
\textit{Acidobacteria} and 1 as \textit{Actinobacteria} (The inset of
Figure~\ref{fig:l2fc} summarizes the Family level taxonomic profile of stable
isotope responders).  Figure~\ref{fig:l2fc} summarizes the ratio of
proportion means for each OTU where means are calculated from proportions in
heavy fractions within labeled or controlled gradients and the ratio is
labeled over control (see methods). If the OTUs are ranked by descending,
moderated proportion mean labeled:control ratios, the top 10 ratios (i.e. the
10 OTUs that were most enriched in the labeled gradients considering only
heavy fractions) are either \textit{Firmicutes} (6 OTUs) or
\textit{Proteobacteria} (4 OTUs).  Figure~\ref{fig:scatter_heavy} shows the
relative abundance values for the top 10 OTUs in heavy fractions of labeled
and control gradients.  Table~\ref{tab:LTP_blast} summarizes the results from
BLAST searching the centroid sequences for these top 10 OTUs against the LTP
database \textit{Proteobacteria} OTU centroid sequences for the top 10
responders all share high identity ($>$98.48\% identity,
Table~\ref{tab:LTP_blast}) with cultivars from genera known to possess
diazotrophs including \textit{Klebsiella}, \textit{Shigella},
\textit{Acinetobacter}, and \textit{Ideonella}. None of the
\textit{Firmicutes} OTUs in the top 10 responders share greater than 97\%
sequence identity with sequences in the LTP database (release 115) (see
Table~\ref{tab:LTP_blast}).

\subsection{Distribution of BSC Diazotrophs in Environmental Samples}
\subsubsection{Non-Cyanobacterial Taxa}
\paragraph{\textbf{\textit{Clostridiacea}:}} Five of the 6
\textit{Firmicutes} in the top 10 responder OTUs (above) belong in the
\textit{Clostridiacea}. We only observed one of these strongly responding
\textit{Clostridiaceae} in the data presented by \citet{Garcia_Pichel_2013},
"OTU.108" (closest BLAST hit in LTP Release 115 -- \textit{Caloramotor
proteoclasticus}, BLAST \%ID 96.94, Accession X90488).  OTU.108 was found in
two samples both characterized as "light" crust. One other
\textit{Clostridiaceae} OTU with a proportion mean ratio (labeled:control)
p-value less than 0.10 but outside the top 10 responders was found in the
\citet{Garcia_Pichel_2013} data and also in a "light" crust sample. None of
the strongly responding \textit{Clostridiacea} were found in the sequences
provided by \citet{Steven_2013}.

Figure~\ref{fig:clost_tree} depicts the phylogenetic breadth of
\textit{Clostridiaceae} $^{15}$N responder OTUs from this experiment. The
phylogenetic tree was constructed from near full-length reference sequences,
and edge width demonstrates the placements of short OTU centroid sequences in
the backbone tree (see methods for description of placement algorithm and
selection criteria for reference sequences). As shown,
\textit{Clostridiaceae} $^{15}$N-responder OTU centroid 16S sequences are
generally more closely related to environmental than cultivar 16S gene
sequences.   

\paragraph{\textbf{\textit{Proteobacteria}:}} Only "OTU.342" (closest
BLAST hit in LTP Release 115, BLAST \%ID 100, Accession ZD3440,
\textit{Acinetobacter johnsonii}) of the \textit{Proteobacteria} OTUs in the
top 10 most strongly responding OTUs was found in the
\citet{Garcia_Pichel_2013} sequences. None of the strongly responding
\textit{Protebacteria} OTUs were found in the \citet{Steven_2013} sequences.
There were 133 responder OTU-sample occurrences (responder OTU was found in a
sample library) in the \citet{Steven_2013} data.  83 were in "below crust"
samples, 50 in BSC samples.

\paragraph{\textbf{Other taxa:}} Two potentially diazotroph OTUs were found
in an extensive number of environmental samples (61 of 65 samples from the
combined data sets of \citet{Garcia_Pichel_2013} and \citet{Steven_2013}).
Both OTUs were annotated as \textit{Acidobacteria} but shared little sequence
identity to any cultivar SSU rRNA gene sequences in the LTP (Release 115),
with best LTP BLAST hits of 81.91 and 81.32\% identity. Additionally, the
evidence for $^{15}$N incorporation for each OTU was weak relative to other
putative responders (adjusted p-values of 0.090 and 0.096). Of the remaining
36 stable isotope responder OTUs, only 14 were observed in the environmental
data.  Figure~\ref{fig:rspndr_dist} summarizes the OTU-sample occurrences in
both the \citet{Steven_2013} and the \citet{Garcia_Pichel_2013} data with
occurrences distributed into the most relevant sample classes of each study.

\subsubsection{Heterocystous \textit{Cyanobacteria}} At least one OTU defined
by \citet{Yeager} sequences (see Table~\ref{table:yeager_2006}) was found in
21 of the 23 \citet{Garcia_Pichel_2013} sampling sites. Counts of samples
with \citet{Yeager} sequence defined heterocystous \textit{Cyanobacteria}
OTUs are summarized in Table~\ref{table:het_dist}. The opposite BSC relative
abundance relationships of \textit{Microcoleus Vaginatus} and \textit{M.
Strenstrupii} with site mean annual temperature was a major finding by
\citet{Garcia_Pichel_2013}.  \citet{Garcia_Pichel_2013} did not report the
relationship of diazotrophic \textit{Cyanobacteria} with temperature although
a comment by \citet{Belnap28062013} briefly discusses a qualitative positive
relationship of \textit{Scytonema} with temperature in the
\citet{Garcia_Pichel_2013} data.  In agreement with the
\citet{Belnap28062013} interpretation, we found a positive relationship of
\textit{Scytonema hyalinum} FGP-7A and DC-A OTU relative abundance with mean
annual temperature (p-values 3.332x10$^{-03}$ and 3.173x10$^{-04}$,
respectively) (Figure~\ref{fig:het_temp}). We also found \textit{Nostoc
commune} MCT-1 and MFG-1 OTU relative abundance was inversely related to mean
annual temperature (p-values 1.307x10$^{-02}$ and 1.577x10$^{-06}$,
respectively) (Figure~\ref{fig:het_temp}). 

\begin{table}

\textbf{
    \refstepcounter{table}
    \label{table:het_dist}
    Table \arabic{table}.
}
    
    {Counts of heterocystous \textit{Cyanobacteria}l OTU occurrences in \citet{Garcia_Pichel_2013} samples (n = 23) and \citet{Steven_2013} samples (n = 42)}

{\centering
\begin{tabular}{lrr}
  \toprule
 Isolate & \citet{Garcia_Pichel_2013} & \citet{Steven_2013} \\ 
  \midrule
Calothrix MCC-3A &   1 &   6 \\ \midrule
Nostoc commune MCT-1 &  16 &  23 \\ \midrule
Nostoc commune MFG-1 &  12 &  23 \\ \midrule
Scytonema hyalinum DC-A &  17 &  30 \\ \midrule
Scytonema hyalinum FGP-7A &  18 &  27 \\ \midrule
Spirirestis rafaelensis LQ-10 &  16 &  30 \\
   \bottomrule
\end{tabular}}{}
\end{table}

At least one \citet{Yeager} sequence defined OTU
(Table~\ref{table:yeager_2006}) was found in 35 of 42 \citet{Steven_2013}
samples. The 7 samples that lacked \citet{Yeager} OTUs were "below crust"
samples.  Table~\ref{table:het_dist} summarizes the counts of
\citet{Steven_2013} samples with \citet{Yeager} sequence defined OTUs. As
expected all of the six OTUs defined by \citet{Yeager} sequences were more
abundant in the crust samples than below crust samples
(Figure~\ref{fig:het_steven}) (maximum p-value for any OTU: 1.96x10$^{-4}$).

\subsection{Richness estimates}
Figure~\ref{fig:rarefaction} (inset) summarizes the fraction of observed OTUs
over total OTUs as estimated by CatchAll for each sample 16S library.
Rarefaction curves for each sample are shown in Figure~\ref{fig:rarefaction}.
Qualitatively, rarefaction curves show below crust samples to be more rich than
BSC samples in the \citet{Steven_2013} data.
